### 2022-05-12 manuscript.Rmd
Add citation for data and code

The data for this study is available via https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8. Note that this link is intended for peer review only and will be replaced with a public link upon acceptance.

@@

The code for this study is available via https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8. Note that this link is intended for peer review only and will be replaced with a public link upon acceptance.

>>>>

The data for this study is available via the [Open Science Framework](https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8) [@enge2022a]. Note that this link is intended for peer review only and will be replaced with a public link upon acceptance.

@@

The data for this study is available via the [Open Science Framework](https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8) [@enge2022a]. Note that this link is intended for peer review only and will be replaced with a public link upon acceptance.
